---
title: CODECHECK certificate 2020-001
output:
  pdf_document:
    toc: false
    includes:
       in_header: preamble.sty
  html_document:
    self_contained: false
    toc: true
    toc_float: false
---


\centerline{\includegraphics[width=4cm]{codecheck_logo.pdf}}

\vspace*{2cm}

```{r rsetup-knitr,eval=TRUE,include=FALSE}
require(knitr)
require(xtable)
require(yaml)
require(tibble)
require(readr)
require(rprojroot)
options(width=60)
opts_chunk$set(cache=FALSE)

yml_file = "codecheck.yml"
root_project = find_root(yml_file)
dest_dir = "outputs/"

yaml_data = read_yaml( file.path(root_project, yml_file) )

outputs_manifest = yaml_data$manifest

## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

## Copy each file mentioned in the manifest into DEST_DIR
dest_files = sapply(outputs_manifest, function(x) {
  src_file  = paste0(root_project, x$file)
  dest_file  = paste0(dest_dir,    basename(x$file))
  file.copy(src_file, dest_file)
  dest_file
})
  
get_outputs = function(outputs_manifest) {
  files = sapply(outputs_manifest, function(x) x$file)
  comments = sapply(outputs_manifest, function(x) x$comment)
  sizes = file.size(dest_files)
  url=sprintf('<a href="%s">%s</a>', dest_files, files)
  table = cbind(files, comments, sizes, url)
  table
}
```

```{r,include=FALSE}
## Temporary hack to make URL
url_it = function(url) {
  url = sub("<", "\\\\url{", url)
  url = sub(">", "}", url)
  url
}
```

```{r,include=FALSE}
summary_entries = list(
  "Title" =            yaml_data$paper$title,
  "Authors" =          yaml_data$paper$authors,
  "Reference" =        yaml_data$paper$reference,
  "Codechecker" =      url_it(yaml_data$codecheck$codechecker),
  "Date of check:" =   yaml_data$codecheck$check_time,
  "Summary:" =         yaml_data$codecheck$summary,
  "Repository:" =      url_it(yaml_data$codecheck$repository))
summary_df = data.frame(Item=names(summary_entries),
                Value=unlist(summary_entries, use.names=FALSE))
```


```{r,echo=FALSE,results='asis'}
##kable(df, booktabs=FALSE, align=c('l', 'p{12cm}'), caption="CODECHECK Summary")
print(xtable(summary_df, align=c('l', 'l', 'p{10cm}'),
             caption='CODECHECK summary'),
      include.rownames=FALSE,
      include.colnames=TRUE,
      sanitize.text.function = function(x){x},
      comment=FALSE)
```




```{r, echo=FALSE,results='asis'}
outputs = get_outputs(outputs_manifest)
xt = xtable(outputs[,1:3], caption="Summary of output files generated")
colnames(xt) = c("File", "Comment", "Size")
print(xt,
      include.rownames=FALSE,
      comment=FALSE)
```


# Summary

The reproduction of the figures in the manuscript was straightforward
given that the authors provided a Rmarkdown document that processed
the results data files.  The results data files were not independently
reproduced at this stage because of the long compute time.



\clearpage

# CODECHECKER notes


### Data and Code

After creating an empty repository, the following data and results
folders were copied from CODE OCEAN capsule (<https://codeocean.com/capsule/5449763/tree>) for the paper: `Datasets`,
`Results_Basic`, `Results_FeatureSelection` and
`Results_ParamsOptimized`.  One of the data files
`Results_ParamsOptimized/diabetes/Nested_Predictions.tsv.gz` needed to
be compressed to reduce the file size from 160 Mb to 9 Mb (Github has
limit on individual files of 100 Mb.)


The main Rmd and helper script were downloaded from
<https://github.com/srp33/ShinyLearner/>.  The Rmd file was edited to
read the compressed version of the .tsv file.

As no MANIFEST was provided by the author, SJE made one.

### Extra software installations



To run this script, I needed to install the following R packages

```{r eval=FALSE}
install.packages("tidyverse")
install.packages("cowplot")
```

### Running the software to regenerate outputs.

A few small edits were made to the `Analyze_Results.Rmd`, see the git
history,

To regenerate the Figures/ folder, we simply ran `make run` in the
Makefile, created by SJE.


\clearpage

<!-- Perhaps yml should note which files should be shown in the -->
<!-- certificate?  By default, figures could be included with -->
<!-- *include_graphics* and data frames could be summarised by the tibble. -->

<!-- todo: script this below... -->

```{r pressure, echo=FALSE, fig.cap=outputs[1:6,"comments"]}
knitr::include_graphics(dest_files[1])
cat('\n\n')
knitr::include_graphics(dest_files[2])
cat('\n\n')
knitr::include_graphics(dest_files[3])
cat('\n\n')
knitr::include_graphics(dest_files[4])
cat('\n\n')
knitr::include_graphics(dest_files[5])
cat('\n\n')
knitr::include_graphics(dest_files[6])
cat('\n\n')
```


\clearpage

## Table 1

```{r}
read_tsv(dest_files[7])
```

\clearpage

## Table 2

```{r}
print(read_tsv(dest_files[8]))
```

\clearpage

# About this document

This document was created using Rmarkdown.  `make codecheck.pdf` will
regenerate the file.

```{r}
sessionInfo()
```



<!-- 
  rmarkdown::render("piccolo2020-codecheck.Rmd", output_format="pdf_document") 
  -->
